---
title: "Homework 2"
author: "Yuxin"
date: "2018.9.29"
output: github_document
---
```{r setup,include=FALSE}
devtools::install_github("p8105/p8105.datasets")
library(tidyverse)
library(dplyr)
library(readxl)
library(p8105.datasets)
```

Problem 1

```{r load_data}
NYC_Tranist <- read.csv("~/data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
NYC_Tranist <- janitor::clean_names(NYC_Tranist)
NYC_Retain <- select(NYC_Tranist,line:vending,ada,ada_notes)
NYC_Retain$entry <- ifelse(NYC_Retain$entry == "YES",TRUE,FALSE)
```

*** This dataset contains several variables which state the information about the specific station. Variables include the name, location, and entrance or vending facilities of the station. So far, we cleaned some redundant variables, including the geographic location of the station, the exit of the station. Also, I changed the name of the variable which makes it more succinct. The dimension of the resulting dataset is `r nrow(NYC_Retain)`. I think these data are tidy since we have variables in columns, observations in Rows, and every value has a cell.

*** Q1 How many distinct stations are there? Note that stations are identified both by name and by line (e.g. 125th St A/B/C/D; 125st 1; 125st 4/5); the distinct function may be useful here.

*** A1: There are `r nrow(distinct (NYC_Retain,line,station_name))` distinct stations according to both name and line.

*** Q2: How many stations are ADA compliant?

*** A2: There are `r  table(NYC_Retain$ada)["TRUE"]` stations are ADA compliant. 

*** Q3: What proportion of station entrances / exits without vending allow entrance?

*** A3: The proportion of station entrances / exits without vending allow entrance is  `r sum(NYC_Retain$vending == "NO" & NYC_Retain$entry == "TRUE")/sum(NYC_Retain$vending == "NO")`

```{r include=FALSE}
attach(NYC_Retain)
NYC_Retain$route1 <-as.character(route1)
NYC_Retain$route2 <-as.character(route2)
NYC_Retain$route3 <-as.character(route3)
NYC_Retain$route4 <-as.character(route4)
NYC_Retain$route5 <-as.character(route5)
NYC_Retain$route6 <-as.character(route6)
NYC_Retain$route7 <-as.character(route7)
detach(NYC_Retain)
```

```{r reform_data}
NYC_Retain = unite(NYC_Retain,Route_name,route1:route11,sep='',remove=TRUE)
NYC_Retain$Route_name = gsub("NA","",NYC_Retain$Route_name)
NYC_Retain = mutate(NYC_Retain,Route_number = nchar(NYC_Retain$Route_name)) %>%
select(line:station_longitude,Route_name,Route_number,everything())
```
*** Q3: How many distinct stations serve the A train?

*** A3: There are `r table(grepl("A",NYC_Retain$Route_name))["TRUE"]` stations serve the A train. 

*** Q4:  Of the stations that serve the A train, how many are ADA compliant?

*** A4: `{r}
filter(NYC_Retain,route1 == "A") %>%
summary(ada)`
We can observe 107 stations which serve the A train that are ADA compliant.


Problem 2

```{r load_TrashWheel Data}
Trash_Wheel <- read_excel("~/data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",range=cell_cols("A:N")) %>%
janitor::clean_names()%>%
filter(!is.na(dumpster))%>%
mutate(sports_balls=as.integer(round(sports_balls)))
Trash_Wheel
```

```{r load_Precipitation2017}
Precipitation_2017 <- read_excel("~/data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",sheet="2017 Precipitation",range="A2:B14") %>%
janitor::clean_names()%>%
filter(!is.na(total))%>%
mutate(year=2017)%>%
select(year,month,total)
Precipitation_2017
```

```{r load_Precipitation2016}
Precipitation_2016 <- read_excel("~/data/HealthyHarborWaterWheelTotals2018-7-28.xlsx",sheet="2016 Precipitation",range="A2:B14") %>%
janitor::clean_names()%>%
filter(!is.na(total))%>%
mutate(year=2016)%>%
select(year,month,total)
Precipitation_2016
```

```{r combine_datasets}
Precipitation_Combine <- merge(Precipitation_2016,Precipitation_2017,by ="month",all=TRUE)%>%
mutate(month = month.name[month])
Precipitation_Combine
```
*** Q1: Be sure to note the number of observations in both resulting datasets, and give examples of key variables.

*** A1: There are 285 observations and 14 variables in Trash Wheel dataset. There are 12 observation and 3 variables in Precipitation 2016,2017. In the trash wheel example, 14 variables basically demonstrate the time(month,year,date) and number label of dumpster(dumpster). It also specify what kind of trash is recorded in the trash wheel. In the precipitation example, dataset recorded the rainfall amount of different month.

*** Q2:For available data, what was the total precipitation in 2017? 

*** A2: The total precitation in 2017 is  `r sum(Precipitation_2017$total)`

*** Q3:What was the median number of sports balls in a dumpster in 2016?

*** A3: The median number of sports balls in a dumpster in 2016 is `r median(Trash_Wheel$sports_balls[116:166])`

Problem 3
```{r read_dataset}
data("brfss_smart2010")
brfss_data <- brfss_smart2010 %>%
janitor::clean_names() %>%
filter(topic == "Overall Health") %>%
select(-class, -topic, -question, -sample_size, -(confidence_limit_low:geo_location)) %>%
spread(key=response,value=data_value) %>%
janitor::clean_names() %>%
mutate(Proportion = excellent+very_good)
brfss_data
```

Q1: How many unique locations are included in the dataset? Is every state represented? What state is observed the most?

A1: There are `r length(unique(brfss_data$locationdesc))` unique locations are included in the dataset. There are `r length(unique(brfss_data$locationabbr))` states covered in the data. Yes, every state is represented. NY state is observed the most with `r max(table(unlist(brfss_data$locationabbr)))` times.

Q2: In 2002, what is the median of the “Excellent” response value?

A2: The median of the "Excellent" response value is 23.6
```{r}
brfss_data %>%
group_by(year)%>%
filter(year == 2002) %>% 
summarize(median_excellent = median(na.omit(excellent)))
``` 
Q3: Make a histogram of “Excellent” response values in the year 2002.

A3:
```{r Problem3_histogram}
ggplot(subset(brfss_data, year == 2002),aes(x=excellent))+geom_histogram()
```


Q4: Make a scatterplot showing the proportion of “Excellent” response values in New York County and Queens County (both in NY State) in each year from 2002 to 2010.
```{r Problem3_scatter}
brfss_data %>%
group_by(locationdesc) %>%
filter(locationdesc == "NY - New York County" |locationdesc == "NY - Queens County") %>%
ggplot(aes(x=year,y=excellent))+geom_point(aes(color = locationdesc))
```

